An exploratory analysis of the influence of resource use on the yield verse quality trade-off in Australian vineyards

### 2023-07-31 article.tex
Minor edits - up to end of results.

In this analysis we observe relationships between yield and quality through the use of linear models. Although an extensive amount of research into a variety of factors' effect on grape quality and yield exists; due to the lack of long-term and in-depth data, individual effects are often studied in isolation \citep{abbalDecisionSupportSystem2016}. The lack of consolidated datasets also restricts the ability to gain statistical insights at large scales and across multiple regions \citep{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. The dataset used for this analysis includes data collected for the past 10 years from a multitude of vineyards located over a diverse range of Australian winegrowing regions.

@@

We aim to use this broad dataset to confirm the existence of a yield verse quality trade off within Australian winegrowing; one not prior confirmed explicitly across such extensive diversities.
% you require a reference here
In achieving this, the context of how resource-use relates to yield and quality will also be described.
% Describing baselines is more important - it needs to be emphasised more so than something that is known but not shown. This is the heart of what your are doing sell it more.
We link these relations to the potential for improvement through decision-making processes, whilst highlighting that the way moving forward will require the optimisation of these processes. The practical addition of these aims is a baseline for comparison - given a vineyard within Australia, one could extrapolate their comparative efficiency with regard to the tradeoff between invested resources, yield and quality.

@@

           & $\mathbf{R^2}$ & $\mathbf{R^2}$ & \textbf{F-Statistic} & \textbf{P-Value} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual\\ Standard Error\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Sum\\ of Squares\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Mean\\ of Squares\end{tabular}} \\ \midrule

@@

@@

For Models 1 (yield) and 3 (value) year played a pivotal role, with only one year in each model not being significant (2021/2022 and 2016/2017 respectively). Both Model 1 and 3 showed a majority of regions were significant with 32 of 54 regions being significant in Model 1, and 42 of 50 regions being significant in Model 3 with 95\% confidence.

@@

With regard to continuous variables, Model 1 and 2 showed water use, scope 1 emissions and area harvested were significant at 95\% confidence when accounting for other variables. T-tests for Model 3 showed all continuous variables except scope 1 emissions were significant. Model 4 showed scope 1 emissions and water use to only be significant when considered as an interaction with area harvested but not when considered on their own.

@@

The coefficients of each model describe the relationship of a predictor variable to its response when considering all other variables. Due to the transformations of the data, coefficients are individually interpreted in the same manner as the prior regression values were (see Section \ref{sec:exp_anal}); unlike the regression values,  coefficient ranges are not limited between -1 and 1, as each variable needs to be considered together.

@@

We look at the coefficients of categorical and continuous variables separately. This is primarily done as the categorical variables have many coefficients, one for each category, whilst continuous variables have only one. The coefficient for categorical variables is summarised in Figure\ref{fig:violin}; illustrating the difference in the range as well as affect region and year could have on each of the models. Comparatively, the continuous variables coefficients are summarised in Table \ref{tab:contvar}.
In terms of magnitude, GI region has the highest possible absolute value for each model. An important consideration is that region and year are binary, such that they are only equal to zero or the coefficient (as they will present as a value of 1 which will be multiplied by the coefficient); this means that, although region may have a strong relationship, it can be overshadowed by an extreme value of one of the continuous variables. The most notable difference between the continuous variables coefficients is the change from positive to negative values. This change occurs between the Models for Yield (Model 1 and 2) and the Models for value (Models 3 and 4); where all but the coefficient for area harvested had the opposite sign. These models also differ in an order of magnitude when looking at resource use, with the coefficients for yield being smaller than those for value. 

@@

\begin{figure}
  \caption{Violin plots of GI Region and Year coefficients for each model.}\label{fig:violin}

@@

>>>>

In this analysis we observe relationships between yield and quality through the use of linear models. An extensive amount of research into a variety of factors' effect on grape quality and yield exists; due to the lack of long-term and in-depth data, individual effects are often studied in isolation \citep{abbalDecisionSupportSystem2016}. The lack of consolidated datasets also restricts the ability to gain statistical insights at large scales and across multiple regions \citep{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. The dataset used for this analysis includes data collected for the past 10 years from a multitude of vineyards located over a diverse range of Australian winegrowing regions.

@@

We aim to use this broad dataset to describe the relationship of input resources to the output yield and quality of vineyards. The practical addition of this aim is a baseline for comparison - given a vineyard within Australia, one could extrapolate their comparative efficiency with regard to the tradeoff between invested resources, yield and quality. In achieving this we will also confirm the existence of a yield verse quality trade off within Australian winegrowing; one not prior confirmed explicitly across such varying regions, scales and climates. 

@@

           & $\mathbf{R^2}$ & \textbf{\begin{tabular}[c]{@{}c@{}} Adjusted\\ $\mathbf{R^2}$ \end{tabular}} & \textbf{F-Statistic} & \textbf{P-Value} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual\\ Standard Error\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Sum\\ of Squares\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Mean\\ of Squares\end{tabular}} \\ \midrule

@@

%b Should this be in the discussion (below para)

@@

For Models 1 (yield) and 3 (value) year played a pivotal role, with only one year in each model not being significant (2021/2022 and 2016/2017 respectively). Both Model 1 and 3 showed a majority of regions were significant with 32 of 54 regions being significant in Model 1, and 42 of 50 regions being significant in Model 3 at 95\% confidence.

@@

With regard to continuous variables: Model 1 and 2 showed all variables to be significant at 95\% confidence when accounting for other variables. T-tests for Model 3 showed all continuous variables except scope 1 emissions were significant. Model 4 showed all variables aside from scope 1 emissions and water use to be significant; with scope 1 emissions and water use only being significant when considered as an interaction with area harvested but not when considered on their own.

@@

The coefficients of each model describe the relationship of a predictor variable to its response when considering all other variables. Due to the transformations of the data, coefficients are individually interpreted in the same manner as the prior regression values were (see Section \ref{sec:exp_anal}); unlike the regression values,  coefficient ranges are not limited between -1 and 1.
%, as each variable needs to be considered together.

@@

We look at the coefficients of categorical and continuous variables separately. This is done as the categorical variables have many coefficients, one for each category, whilst continuous variables have only one. The coefficient for categorical variables is summarised in Figure \ref{fig:violin}; illustrating the difference in the range as well as affect region and year could have on each model. Comparatively, the continuous variables coefficients are summarised in Table \ref{tab:contvar}.
In terms of magnitude, GI region has the highest possible absolute value for each model. An important consideration is that region and year are binary, such that they are only equal to zero or the coefficient (as they will present as a value of 1 which will be multiplied by the coefficient); this means that, although region may have a strong relationship, it can be overshadowed by an extreme value of one of the continuous variables. The most notable difference between the continuous variables coefficients is the change from positive to negative values. This change occurs between the Models for Yield (Model 1 and 2) and the Models for value (Models 3 and 4); where all but the coefficient for area harvested had the opposite sign (see Table \ref{contvar}). These models also differ in an order of magnitude when looking at resource use, with the coefficients for yield being smaller than those for value. 

@@

\begin{figure}\label{fig:violin}

@@

  \caption{Violin plots of GI Region and Year coefficients for each model.}
